Pteropod physiological analysis

### 2018-03-29 figures.Rmd
switch axis fig 4

# mod 4 physio (abu, o2, pco2 - pos additive)
pl4 <- filter(physel, grepl('4$', Model)) %>% 
  .$Modobj %>% 
  .[[1]] %>% 
  get_pldat(., 'O2', fct = 0.85)

p4 <- ggplot() +
  geom_line(data = pl4[[1]], aes(x = pCO2, y = abu, group = O2, colour = O2), size = 1) + 
  geom_text(data = pl4[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('Abundance') +
  ggtitle("(a) Synergistic effect of O2 on\npCO2 stress")

>>>>

# mod 4 physio (abu, o2, pco2 - pos additive)
pl4 <- filter(physel, grepl('4$', Model)) %>% 
  .$Modobj %>% 
  .[[1]] %>% 
  get_pldat(., 'pCO2', fct = 0.9)

p4 <- ggplot() +
  geom_line(data = pl4[[1]], aes(x = O2, y = abu, group = pCO2, colour = pCO2), size = 1) + 
  geom_text(data = pl4[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('Abundance') +
  ggtitle("(a) Synergistic effect of O2 on\npCO2 stress")
